\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-02 Final Paper/PaperJLin.tex
Moved tables
Added tables

% Table for D1015 - election type
%\begin{table}
%	\centering
	%\resizebox{\columnwidth}{!}
	%\def\arraystretch{1.5}
%	\caption{\tb{Types of Election by Polity}}
%	\begin{tabulary}{\textwidth}{l c c c c} 
%		\hline
%		\tb{Country}&\tb{Year}&\tb{Legislative}&\tb{Both}&\tb{Presidential}\\
%		\hline
%		Argentina&2015&-&X&-\\
%		Australia&2013&X&-&-\\
%		Austria&2013&X&-&-\\
%		Bulgaria&2014&X&-&-\\
%		Czech Republic&2013&X&-&-\\
%		Finland&2015&X&-&-\\
%		France&2012&-&-&X\\
%		Germany&2013&X&-&-\\ 
%		Great Britain&2015&X&-&-\\
%		Greece&2012/2015&X&-&-\\
%		Iceland&2013&X&-&-\\
%		Ireland&2011&X&-&-\\
%		Israel&2013&X&-&-\\
%		Japan&2013&X&-&-\\
%		Kenya&2013&-&X&-\\
%		Latvia&2011/2014&X&-&-\\
%		Mexico&2012&-&X&-\\
%		Mexico&2015&X&-&-\\
%		Montenegro&2012&X&-&-\\
%		Norway&2013&X&-&-\\
%		New Zealand&2011/2014&X&-&-\\
%		Peru&2016&-&X&-\\
%		Philippines&2016&-&X&-\\
%		Poland&2011&X&-&-\\
%		Portugal&2015&X&-&-\\	
%		Romania&2012&X&-&-\\
%		Romania&2014&-&-&X\\
%		Serbia&2012&-&X&-\\
%		Slovakia&2016&X&-&-\\
%		Slovenia&2011&X&-&-\\
%		South Africa&2014&X&-&-\\ 
%		South Korea&2012&X&-&-\\
%		Sweden&2014&X&-&-\\
%		Switzerland&2011&X&-&-\\
%		Turkey&2015&X&-&-\\
%		\hline
%	\end{tabulary} \\
%	\e{Source:} Comparative Study of Electoral Systems Module IV 
%	\label{table1}
%\end{table}

%Brazil&2014&-&X&-\\
%Canada&2011&X&-&-\\
%Canada&2015&X&-&-\\
%Hong Kong&2012&X&-&-\\
%United States&2012&-&X&-\\
%Taiwan&2012&-&X&-\\
%Thailand&2011&X&-&-\\

%Table \ref{table1} shows the types of elections that are held within each of the polities that are represented in the Comparative Study of Electoral Systems Module IV data. From this table, we see that many of the countries are holding legislative, or parliamentary elections to some extent during the period between 2011 and 2016. This table provides some background for the context in each of the polities that will be included in the analysis.

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Worldwide} \\
			\hline
			Small Town&-.1338***  \\    
			& (.0336)   \\
			Suburban & -.2591***\\ 
			& (.0358) \\
			Urban   & -.0482   \\
			& (.0300)    \\
			Constant   & 5.597***  \\
			&(.0234) \\
			N  & 47,821  \\
			$R^2$	& 0.0011 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table3}
	\end{table}
\end{singlespace}

@@

%Southwestern Europe

@@

%Self Placement Column Changed
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &.0231&-.0018 \\
	&(.0519)&(.0130) \\
	Suburban& .0555***& .0147 \\
	&(.0688)& (.0157) \\
	Urban&.1214** & -.0420*** \\
	&(.0507) & (.0117) \\
	\e{Democracy}& -.1599*** & -.0421***\\
	&(.0190) & (.0040)\\
	\e{Regime Age} & .0013 &  -.0075***\\
	&(.00027) & (.0001)\\
	\e{Electoral Formula}&.0789*** & -.0440***\\
	&(.0302) & (.0070) \\
	\hline
	Constant& 6.510*** & 6.5149*** \\
	&(.2067) & (.0391)\\
	N&18748 & 41,373 \\
	$R^2$&0.0406& 0.1273 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[h!]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.6640*** &.0608 &-.1600** \\
		&(.0766)&(.0435) &(.0727) \\
		Suburban&-.6389*** &-.1894***&-.1260  \\
		&(.1042) &(.0451) &(.1180) \\
		Urban&-.5781*** &-.0327 &.2655*** \\
		&(.0710) &(.0388) &(.0644) \\
		Constant& 5.8256*** &5.5408***&5.5562*** \\
		&(.0543) &(.0297) &(.0531) \\
		Countries&5&21&6 \\
		N&8,350&28,869 &10,602 \\
		$R^2$&0.0114&0.0011 &0.0052 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

@@

\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Variables Used in Analyses}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Variable Name}& \tb{Variable Number} & \tb{Description}&\tb{Outside Source} \\
		\hline
		Election ID Variable &D1004&Polity and Election Year&-\\
		Place of Residence&D2031&Rural or Urban Residence&-\\
		Left-Right Self&D3014&Self-rate ideology &-\\
		Age&D2001\_Y&2018-VAR-Value&- \\
		Gender&D2002&Gender of Respondent&- \\
		Education&D2003&Highest Education Attained&- \\
		Socioeconomic Status&D2012&SES&- \\
		Religiosity&D2025&Identifies with religion?&-  \\
		Party ID&D3018\_3&Party Closest to R&- \\
		Closeness&D3018\_4&Party attachment&- \\
		Level of Democracy&D5051\_1&Democracy-Autocracy at Election&Polity IV Project\\
		Age of Current Regime&D5052&Age of Regime in Years& Polity IV Project\\
		Electoral Formula&D5058&Method of Election&CSES Macro Report\\
		\hline
	\end{tabulary}\\
	\e{Source:} Comparative Study of Electoral Systems Module IV Codebook available at \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}
	\label{table99}
\end{table}

@@

\begin{singlespace}
\begin{table}[H]
	\centering
	\def\arraystretch{1}
	\caption{\tb{General Trends of Ideology}}
	\begin{tabulary}{\linewidth}{l c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Self-Placement} & \tb{Liberalism} \\
		\hline
		Small Town&-.1338***& -.1005*** \\    
		& (.0336) & (.0136)  \\
		Suburban & -.2591*** &-.1737 ***\\ 
		& (.0358) &(.0162) \\
		Urban   & -.0482 &-.1309***  \\
		& (.0300)  &(.123)  \\
		Constant   & 5.597*** &5.7164*** \\
		&(.0234) & (.0093)\\
		N  & 47,821 & 42,500 \\
		$R^2$	& 0.0011 & 0.0037 \\
		\hline                                       
	\end{tabulary}
	\\
	\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
	\e{Reference:} A rural place of residence serves as the baseline for comparison
	\label{table102}
\end{table}
\end{singlespace}

>>>>

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Worldwide} \\
			\hline
			Small Town&.1647**  \\    
			& (..0722)   \\
			Suburban & .2714***\\ 
			& (.0934) \\
			Urban   & .2679***   \\
			& (.0721)    \\
			Constant   & 5.1086***  \\
			&(.1993) \\
			N  & 10,548  \\
			$R^2$	& 0.0454 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table3}
	\end{table}
\end{singlespace}

@@

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}
			\\
			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town&.2627 &-.0542 &-.3076 & -1.3042** & .0309 & .0511\\
			&(.3319)& (.5039) & (.4971) & (.5882) & (.3619) & (.6030)\\
			Suburban& .3400 & -.8706 &-.3540 & -.2289  &.2880 &.7052\\
			& (.2941) &(.4878) & (.5298) & (.8432) & (.8747) & (.7604)\\
			Urban& -.2833& -.8586** & -.3762 & .1149& 1.1965** & -.9908\\
			& (.4204)& (.3852) & (.4642) & (1.1020) & (.3769) & (.8057)\\
			Constant& 11.310*** &3.7549*** & 2.2395*** &7.633*** & 5.1379*** & 6.262***\\
			& (.9980) & (1.2241)  & (.9403) & (2.1586)& (1.3297) & (2.300)\\
			N& 440 & 360 & 476 & 152 & 566 &245\\
			$R^2$&0.5188 &0.1740& 0.1346 &0.1939& 0.0313 &0.1064 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table8}
	\end{table}
\end{landscape}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Eastern Europe}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
			\hline
			Small Town &.0423 &-.1924 \\
			&(.5399) & (.4346) \\
			Suburban&- & -.1413 \\
			& - & (.5755) \\
			Urban&-.3829&-.3400 \\
			& (.4270) & (.3978) \\
			Constant & 5.502*** &7.8918*** \\
			& (1.4972) & (1.146) \\
			N&188 & 276\\
			$R^2$& 0.1469 &0.0424 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table9}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.5796 & .4447 \\
			&(.3041)  & (.6314)\\
			Suburban&.5968 &.3318 \\
			& (.3478)  & (.6740)\\
			Urban &- & .4440\\
			&- & (.5626)\\
			Constant& 61311*** &1.953 \\
			& (.9217)  & (.1.813)\\
			N&439 & 251\\
			$R^2$&0.2978 & 0.1484 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table10}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Africa}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-1.0519** \\
			&(.4499)\\
			Constant&8.7909*** \\
			& (1.5955) \\
			N& 220\\
			$R^2$&.0660 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table11}
	\end{table}
\end{singlespace}

\begin{singlespace}
	\begin{table}[H]
		\centering 
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Asia}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
			\hline
			Small Town &.6578** & -.5849 \\
			&(.2648) & (.4634)\\
			Suburban&.5867** & -2.233*** \\
			& (.2796) & (.7757)\\
			Urban & .6344** &.0059 \\
			& (.2576) & (4217)\\
			Constant& 6.0168*** & .4540 \\
			& (.7272) & (1.495)\\
			N&528 & 267\\
			$R^2$&0.0886 & 0.2113\\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table12}
	\end{table}
\end{singlespace}

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town & -.3603  & .6010  \\      
			& (.3050) & (.8141)    \\
			Suburban  & -   & .7878  \\ 
			 & -   & (1.4391)       \\
			Urban  & -.0154   & .3447 \\
			 &(.2926)   & (.4770)      \\
			Constant  & 5.176***  & 7.838***   \\
			&(.8503)&(1.8952) \\
			N  &586 & 115  \\
			$R^2$  &0.0491  &0.0627     \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table13}
	\end{table}
\end{landscape}

@@

%Self Placement and Liberalism Column Changed
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &.0231&-.0151 \\
	&(.0519)&(.0271) \\
	Suburban& .0555***& -.0777** \\
	&(.0688)& (.0350) \\
	Urban&.1214** & .0598 \\
	&(.0507) & (.0267) \\
	\e{Democracy}& -.1599*** & .0153\\
	&(.0190) & (.0088)\\
	\e{Regime Age} & .0013 & .0086***\\
	&(.00027) & (.0003)\\
	\e{Electoral Formula}&.0789*** & .0744***\\
	&(.0302) & (.0151) \\
	\hline
	Constant& 6.510*** & 2.335*** \\
	&(.2067) & (.1012)\\
	N&18,748 & 9,292 \\
	$R^2$&0.0406& 0.0930 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

\begin{table}[h!]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.2413 &.3437*** &.0425 \\
		&(.1583)&(.0982) &(.1377) \\
		Suburban&-.0981 &.2715**&.4923**  \\
		&(.2307) &(.1174) &(.2124) \\
		Urban&-.3787* &.1999** &.5009*** \\
		&(.1995) &(.0981) &(.1298) \\
		Constant& 1.776*** &5.3337***&5.9321*** \\
		&(.5730) &(.2616) &(.3651) \\
		N&1,440&6,057 &3,043\\
		$R^2$&0.1375&0.0549&0.0221 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

@@

\begin{table}[h!]
	\centering
	\def\arraystretch{1.3}
	\caption{\tb{Variables Used in Analyses}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Variable Name}& \tb{Variable Number} & \tb{Description}&\tb{Outside Source} \\
		\hline
		Election ID Variable &D1004&Polity and Election Year&-\\
		Place of Residence&D2031&Rural or Urban Residence&-\\
		Left-Right Self&D3014&Self-rate ideology &-\\
		Age&D2001\_Y&2018-VAR-Value&- \\
		Gender&D2002&Gender of Respondent&- \\
		Education&D2003&Highest Education Attained&- \\
		Socioeconomic Status&D2012&SES&- \\
		Religiosity&D2025&Identifies with religion?&-  \\
		Party ID&D3018\_3&Party Closest to R&- \\
		Closeness&D3018\_4&Party attachment&- \\
		Level of Democracy&D5051\_1&Democracy-Autocracy at Election&Polity IV Project\\
		Age of Current Regime&D5052&Age of Regime in Years& Polity IV Project\\
		Electoral Formula&D5058&Method of Election&CSES Macro Report\\
		\hline
	\end{tabulary}\\
	\e{Source:} Comparative Study of Electoral Systems Module IV Codebook available at \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}
	\label{table99}
\end{table}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Self-Placement}&\tb{Liberalism} \\
			\hline
			Small Town&.1647**&.0432  \\    
			& (..0722) &(.0278)  \\
			Suburban & .2714*** &.0082\\ 
			& (.0934) &(.0352) \\
			Urban   & .2679*** &.0995***  \\
			& (.0721)  &(.0272)  \\
			Constant   & 5.1086*** &2.7915*** \\
			&(.1993)&(.0762)  \\
			N  & 10,548 &9.662  \\
			$R^2$	& 0.0454&0.0195 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table102}
	\end{table}
\end{singlespace}
